The analogy of the cohort-equations paradigm to the compartmental epidemic models

### 2021-05-19 cohort.tex
minor edits

The matrix form of the cohort framework consists of the following 3 steps.
\begin{enumerate}[{\it step 1}]
\item
write the cohort Eq. 
\begin{equation}
\label{eq:cohort}
\vec I'=-V \vec I,
\end{equation}
 with the proper initial condition $I(0)$, where the n-by-n matrix $V$ is the flow matrix of leaving infected compartments in \cite{van2002reproduction}.

\item 
finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus
the solution would be 
\begin{equation}
\label{eq:I}
\vec I(\tau) = \exp(-V\tau) \vec I(0).
\end{equation}
The kernel will be 
\begin{equation}
\label{eq:kernel}
\vec K(\tau) = F \vec I(\tau), 
\end{equation}
where $F$ is the matrix of new infections in the compartment framework.
Note that the n-by-n matrix $\exp(-V\tau)$ is the probability of being infected and stay infectious at time $\tau$. 
% where $\exp(-V\tau)=\sum_{n=0}^\infty \tau^n (-V)^n/n!$.

@@

\subsection {Simple SIR}
The cohort analogy of a simple SIR compartmental model where $\dot I=\beta S I/N-\gamma I$. The cohort framework is via the cohort Eq. with the following steps.
{\it step 1;} write the cohort Eq. $I'=-\gamma I$ with the initial condition $I(0)=1$, 
{\it step 2;} finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus $k(\tau)=\beta \exp(-\gamma \tau)$.
{\it step 3;} $\R$ will be the integration of the kernel. That is $\R=\beta/\gamma$.

>>>>

The matrix form of the cohort framework consists of the following 3 steps.
\begin{enumerate}[{\it Step 1.}]
\item
Form the cohort Eq. 
\begin{equation}
\label{eq:cohort}
\vec I'=-V \vec I,
\end{equation}
 with the proper initial condition $I(0)$, where the n-by-n matrix $V$ is the flow matrix of leaving infected compartments in \cite{van2002reproduction}.

\item 
Finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus
the solution would be 
\begin{equation}
\label{eq:I}
\vec I(\tau) = \exp(-V\tau) \vec I(0).
\end{equation}
The kernel will be 
\begin{equation}
\label{eq:kernel}
\vec K(\tau) = F \vec I(\tau), 
\end{equation}
where $F$ is the matrix of new infections in the compartment framework.
Note that the n-by-n matrix $\exp(-V\tau)$ is the probability of being infected and stay infectious at time $\tau$. 
% where $\exp(-V\tau)=\sum_{n=0}^\infty \tau^n (-V)^n/n!$.

@@

\subsection {Simple SIR}
The cohort analogy of a simple SIR compartmental model where $\dot I=\beta S I/N-\gamma I$. The cohort framework is via the cohort Eq. with the following steps.
{\it Step 1;} write the cohort Eq. $I'=-\gamma I$ with the initial condition $I(0)=1$, 
{\it Step 2;} finding the intrinsic infectiousness kernel by integrating the cohort Eq. and solving for its time evolution, thus $k(\tau)=\beta \exp(-\gamma \tau)$.
{\it Step 3;} $\R$ will be the integration of the kernel. That is $\R=\beta/\gamma$.
